Secure Composition of Robust and Optimising Compilers

### 2023-06-13 popl/main.tex
Add \MKin macro. Minor grammar fix.

\begin{center}\small\it
	{In the following, we use syntax highlighting accessible to both colourblind and black \& white readers~\citep{patrignani2020use}. 
	Specifically, we use a $\src{blue}$, $\src{sans\text{-}serif}$ font for our $\src{source}$,
	a $\trg{red}$, $\trg{bold}$ font for our $\trg{intermediate}$, 
	and a $\obj{green}$, $\obj{teletype}$ font for $\obj{target}$ language.
	}
\end{center}
\end{abstract}

>>>>

\begin{center}\small\it
	{In the following, we use syntax highlighting accessible to both colourblind and black \& white readers~\citep{patrignani2020use}. 
	Specifically, we use a $\src{blue}$, $\src{sans\text{-}serif}$ font for our $\src{source}$,
	a $\trg{red}$, $\trg{bold}$ font for our $\trg{intermediate}$, 
	and a $\obj{green}$, $\obj{teletype}$ font for our $\obj{target}$ language.
	}
\end{center}
\end{abstract}
